Embedding Dimension of Polyhedral Losses

### 2020-01-30 colt-20/embed-dim.tex
Jessie pass on examples section

\bo{I think around here we want a setup of the QFP where we introduce our specific notation like $x^{ij}_i$.}

\bo{We need to prove the dumb case that it won't be feasible to set $v_i = v_j$.}

>>>>

\bo{I think around here we want a setup of the QFP where we introduce our specific notation like $x^{ij}_i$.}
\jessie{Pass here:}
In studying the Quadratic Feasibility Program (QFP) for specific examples, we find it helpful to think of $X$ as a set of vectors, rather than a matrix.
Specifically, for the $\ellabs{\alpha}$, we denote $X^m$ by $x^{ij}$, where $p^m$ is the distribution of support $2$ putting weight $1-\alpha$ on outcome $i$, and weight $\alpha$ on outcome $j$.
As the convex hull of a finite number of these distributions can be used to describe the abstain cell, we can simplify our QFP by studying these elements of the $X$ matrix, and getting rid of each other $x^{ij}_q$, for $q \neq i,j$, since these do not appear in the constraints.
Observe that each $x^{ij}$ is a matrix, and we denote $x^{ij}_i$ as the $i^{th}$ column\jessie{?} of the matrix $x^{ij}$.
When we look at a specific inner product, then we have $\inprod{v_i}{x^{ij}_y} \leq B_{iy}$.
\jessie{With how I wrote this, might be helpful to index the QFP with $m$.  Feel free to change though.}

\bo{We need to prove the dumb case that it won't be feasible to set $v_i = v_j$.}
\jessie{Pass here:}
For the QFP applied to the $\abstain{1/2}$ property and cell $\gamma_\bot$, we want to claim that for any two $v_i$, $v_j$, we cannot set $v_i = c v_j$ for $c > 0$.
To see this, consider that there is an open halfspace through the origin strictly containing the feasible regions $F_i = \{x : \inprod{v_i}{x} \leq -1, \inprod{v_j}{x} \leq 1 \forall j \neq i\}$ and $F_j$, so there is no set of witnesses such that $x^{ij}_i = -x^{ij}_j$, and therefore the vertex condition is not satisfied for $p^{ij}$.
Thus we cannot have normals $v_i = c v_j$ for $c > 0$.
